D3064R0: Bringing the Laws of Physics to Bear on the OOTA Problem

### 2024-01-11 ootavacuous.tex
Add conjecture on tools and complex OOTA cycles
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

@@

In both
Listings~\ref{lst:OOTA Multiplication Example, Initial Value Zero}
and~\ref{lst:OOTA Conditional Multiplication Example, Initial Value Zero},
an OOTA cycle would need to affect both the \co{x} and the \co{y} branches
of this compound semantic dependency.

>>>>

Note that in a C++ implementation that (erroneously) permitted an OOTA
cycle to form, that cycle would involve both \co{r0} and \co{r1}.
However, we conjecture that tools designed to find OOTA cycles could
satisfy themselves with having found either of the two resulting cycles.

@@

In both
Listings~\ref{lst:OOTA Multiplication Example, Initial Value Zero}
and~\ref{lst:OOTA Conditional Multiplication Example, Initial Value Zero},
an OOTA cycle would need to affect both the \co{x} and the \co{y} branches
of this compound semantic dependency.
However, we again conjecture that tools designed to find OOTA cycles could
satisfy themselves with having found either of the two resulting cycles.
